About the Beamer class in presentation making

### 2020-06-25 slides/slides.tex
Update paper and slides

\documentclass{beamer}
\usepackage[utf8]{inputenc}

\usepackage{utopia} %font utopia imported

@@

%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\title[About Beamer] %optional
{About the Beamer class in presentation making}

@@

\author[Arthur, Doe] % (optional)
{A.~B.~Arthur\inst{1} \and J.~Doe\inst{2}}

\institute[VFU] % (optional)
{
  \inst{1}%
  Faculty of Physics\\
  Very Famous University
  \and
  \inst{2}%
  Faculty of Chemistry\\
  Very Famous University
}

\date[VLC 2014] % (optional)
{Very Large Conference, April 2014}

%End of title page configuration block
%------------------------------------------------------------

%------------------------------------------------------------
%The next block of commands puts the table of contents at the 
%beginning of each section and highlights the current section:

@@

%The next statement creates the title page.
\frame{\titlepage}

%---------------------------------------------------------
%This block of code is for the table of contents after
%the title page
\begin{frame}
\frametitle{Table of Contents}
\tableofcontents
\end{frame}
%---------------------------------------------------------

\section{First section}

%---------------------------------------------------------
%Changing visivility of the text
\begin{frame}
\frametitle{Sample frame title}
This is a text in second frame. For the sake of showing an example.

\begin{itemize}
    \item<1-> Text visible on slide 1
    \item<2-> Text visible on slide 2
    \item<3> Text visible on slides 3
    \item<4-> Text visible on slide 4
\end{itemize}
\end{frame}

%---------------------------------------------------------

%---------------------------------------------------------
%Example of the \pause command
\begin{frame}
In this slide \pause

the text will be partially visible \pause

And finally everything will be there
\end{frame}
%---------------------------------------------------------

\section{Second section}

%---------------------------------------------------------
%Highlighting text
\begin{frame}
\frametitle{Sample frame title}

In this slide, some important text will be
\alert{highlighted} because it's important.
Please, don't abuse it.

\begin{block}{Remark}
Sample text
\end{block}

\begin{alertblock}{Important theorem}
Sample text in red box
\end{alertblock}

\begin{examples}
Sample text in green box. The title of the block is ``Examples".
\end{examples}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Two columns
\begin{frame}
\frametitle{Two-column slide}

\begin{columns}

\column{0.5\textwidth}
This is a text in first column.
$$E=mc^2$$
\begin{itemize}
\item First item
\item Second item
\end{itemize}

\column{0.5\textwidth}
This text will be in the second column
and on a second tought this is a nice looking
layout in some cases.
\end{columns}
\end{frame}
%---------------------------------------------------------

>>>>

\documentclass{beamer}

\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{utopia}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{siunitx}
\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}

@@

%------------------------------------------------------------
\title[About Beamer]
{About the Beamer class in presentation making}

@@

\author[Claudio, Jos\'e]
{Claudio Scheer\inst{1} \and Jos\'e Fernando Possebon\inst{1}}

\institute[PUCRS]
{
  \inst{1}%
  Pontifical Catholic University of Rio Grande do Sul - PUCRS\\
  \{claudio.scheer, jose.possebon\}@edu.pucrs.br
}

\date[Deep Learning 2020]
{Deep Learning, June 2020}

@@

\frame{\titlepage}

%---------------------------------------------------------
\begin{frame}
  \frametitle{Table of Contents}
  \tableofcontents
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
\section{Proposal}

\begin{frame}
  \frametitle{Proposal}

  % \begin{itemize}
  %   \item<1-> Text visible on slide 1
  %   \item<2-> Text visible on slide 2
  %   \item<3> Text visible on slides 3
  %   \item<4-> Text visible on slide 4
  % \end{itemize}
\end{frame}

% \begin{frame}
%   In this slide \pause

%   the text will be partially visible \pause

%   And finally everything will be there
% \end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
\section{Dataset}

\begin{frame}
  \frametitle{The Enron Email Dataset}

  {\scriptsize
    no, i dont mind.       : - )
    \bigbreak
    -----Original Message-----
    \bigbreak
    Hi how are you doing?  I have a meeting from 4 to 5, do you mind waiting for me?  Thanks.

    John
    \bigbreak
    -----Original Message-----
    \bigbreak
    hello
  }
\end{frame}

\begin{frame}
  \frametitle{The Enron Email Dataset}

  \begin{itemize}
    \item \href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails};
    \item Get only emails with less than 256 characters;
  \end{itemize}

  \bigbreak
  \bigbreak
  \bigbreak

  Final dataset: \num{40062} input-target pairs.
  \\
  Train dataset: \num{10002} input-target pairs.
\end{frame}

\begin{frame}
  \frametitle{Samples}

  \begin{table}
    \centering
    \begin{tabularx}{\textwidth}{|X|X|}
      \hline
      \textbf{Input}                                                            & \textbf{Target}                                                                       \\
      \hline
      I thought this one was canceled. So I declined to get it off my calendar. & You're right.                                                                         \\
      \hline
      Rex - thanks for the quick response...please note the revised letters below.
      Previous email had a clerical error                                       & Who will sign theses?                                                                 \\
      \hline
      Where can I get info on safety statistics for the pipes?                  & Ralph, please get with Rod and provide what ever he needs in the way of Safety Stats. \\
      \hline
    \end{tabularx}
  \end{table}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
\section{BERT}

\begin{frame}
  \frametitle{BERT architecture}
\end{frame}

\begin{frame}
  \frametitle{Hugging Face}

  \begin{itemize}
    \item BERT base was used;
          \begin{itemize}
            \item 12 layers;
          \end{itemize}
    \item Hugging Face and PyTorch was used;
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Learning Rate Schedule}

  \begin{itemize}
    \item Warm-up steps: \num{10000};
    \item Learning rate: \num{1e-4};
  \end{itemize}

  \bigbreak
  \bigbreak

  \includegraphics[width=\textwidth]{../latex-data/images/warmup_linear_schedule.png}
\end{frame}

\begin{frame}
  \frametitle{Optimizer and hyperparameters}

  \begin{itemize}
    \item Adam;
          \begin{itemize}
            \item Adam epsilon: \num{1e-4};
          \end{itemize}
    \item Batch size: \num{8};
    \item Training epochs: \num{32};
    \item Beam search hypothesis: \num{3};
  \end{itemize}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
\section{Results}

\begin{frame}
  \frametitle{Generated replies}

  \begin{table}
    \centering
    \begin{tabularx}{\textwidth}{|X|X|c|}
      \hline
      \textbf{Email}                      & \textbf{Reply}                                                                              & \textbf{AI?} \\
      \hline
      Shall we have the meeting tomorrow? & meeting is postponed because the 3 : 00 p. m. meeting today. meeting is canceled for today. & \num{30}{\%} \\
      \hline
      hi                                  & Hi how are you?                                                                             & \num{10}{\%} \\
      \hline
      you look so handsome today          & why thank you, you do as well                                                               & \num{30}{\%} \\
      \hline
    \end{tabularx}
  \end{table}
\end{frame}
%---------------------------------------------------------
